Life in the canopy: Phylogenetic filtering and morphological canalization in epiphytic ferns

### 2019-08-06 si/SI.rmd
Update MS, SI

**Table S5** Best-fitting models explaining community diversity metrics by climate and growth habit. Models within delta AICc 3 of the best-fitting model shown. Abbreviations: FDiv, functional diversity; FEve, functional evenness; FRic, functional richness; MPD, mean phylogenetic distance; MNTD, mean nearest taxon distance; VPD, vapor pressure deficit, SD, standard deviation; AICc, corrected Akaike Information Criterion. Values of MPD and MNTD are the standard effect sizes calculated from comparison of observed values with null distribution (see Methods). Trait names refer to community-weighted mean values (see Methods).

```{r best-fit-mods}
# Format and write out table as CSV file
best_fit_div_models %>%
  mutate(resp_var = factor(
        resp_var, 
        levels = c("ntaxa", "mpd.obs.z", "mntd.obs.z", 
                   "FDiv", "FEve", "FRic",
                   "dissection", "sla", "stipe", "pinna"))) %>%
  mutate(
    resp_var = lvls_revalue(
        resp_var, 
        new_levels = c("Richness", "MPD", "MNTD", 
                       "FDiv", "FEve", "FRic",
                       "Dissection", "SLA", "Stipe length", "Pinna no.")) 
  ) %>%
  arrange(resp_var, delta_AICc) %>%
  mutate(
    modname = modname %>%
      str_replace_all("\\+", " \\+ ") %>%
      str_replace_all("\\.by\\.", " × ") %>%
      str_replace_all("habit", "Growth habit") %>%
      str_replace_all("temp_mean", "Mean temp.") %>%
      str_replace_all("temp_sd", "SD temp.") %>%
      str_replace_all("temp_max", "Max. temp.") %>%
      str_replace_all("vpd_mean", "Mean VPD") %>%
      str_replace_all("vpd_sd", "SD VPD") %>%
      str_replace_all("vpd_min", "Min. VPD")
  ) %>% 
  select(
    `Metric` = resp_var,
    `Model` = modname,
    AICc,
    `R2` = r2,
    delta_AICc
  ) %>%
  write_csv(here::here("si/Table_S5.csv"))
```

>>>>

**Table S5** Best-fitting models explaining community diversity metrics by climate and growth habit. Models within delta AICc 3 of the best-fitting model shown. Abbreviations: MPDphy, standard effect size of mean phylogenetic distance; MNTDphy, standard effect size of mean nearest taxon distance; MPDfunc, standard effect size of mean functional distance; MNTDfunc, standard effect size of mean nearest functional distance; VPD, vapor pressure deficit, SD, standard deviation; AICc, corrected Akaike Information Criterion. Trait names refer to community-weighted mean values (see Methods). Frond length and width were highly correlated with rhizome diameter and not shown. For details on calculations of MPD and MNTD, see Methods.

```{r best-fit-mods}
# Format and write out table as CSV file
best_fit_div_models %>%
  # Drop frond length and width (highly correlated with rhizome dia.)
  filter(resp_var %in% c("ntaxa", "mpd.obs.z.phy", "mntd.obs.z.phy", 
                   "mpd.obs.z.func", "mntd.obs.z.func",
                   "dissection", "sla", "stipe", "rhizome", "pinna")) %>%
  mutate(resp_var = factor(
        resp_var, 
        levels = c("ntaxa", "mpd.obs.z.phy", "mntd.obs.z.phy", 
                   "mpd.obs.z.func", "mntd.obs.z.func",
                   "dissection", "sla", "stipe", "rhizome", "pinna"))) %>%
  mutate(
    resp_var = lvls_revalue(
        resp_var, 
        new_levels = c("Richness", "MPDphy", "MNTDphy", 
                       "MPDfunc", "MNTDfunc",
                       "Dissection", "SLA", "Stipe length", "Rhizome diam.", "Pinna no.")) 
  ) %>%
  arrange(resp_var, delta_AICc) %>%
  mutate(
    modname = modname %>%
      str_replace_all("\\+", " \\+ ") %>%
      str_replace_all("\\.by\\.", " x ") %>%
      str_replace_all("habit", "Growth habit") %>%
      str_replace_all("temp_mean", "Mean temp.") %>%
      str_replace_all("temp_sd", "SD temp.") %>%
      str_replace_all("temp_max", "Max. temp.") %>%
      str_replace_all("vpd_mean", "Mean VPD") %>%
      str_replace_all("vpd_sd", "SD VPD") %>%
      str_replace_all("vpd_min", "Min. VPD")
  ) %>% 
  select(
    `Metric` = resp_var,
    `Model` = modname,
    AICc,
    `R2` = r2,
    delta_AICc
  ) %>%
  write_csv(here::here("si/Table_S5.csv"))
```
